Boutiques: a flexible framework for automated application integration in computing platforms

### 2016-11-11 paper.tex
Corrections in 3.1.1

CBRAIN~\cite{SHER-14} is a web platform that can process data
distributed into multiple storage locations on computing clusters and
clouds. CBRAIN offers transparent access to remote data sources,
distributed computing sites, and an array of processing and
visualization tools within a controlled, secure environment.  The
CBRAIN service deployed at the Montreal Neurological Institute relies
on the infrastructure provided by Compute Canada~\cite{das2016mni}. It
currently provides 460+ collaborators in 20 countries with web access
to several systems, including 6 clusters of the Compute Canada
high-performance computing infrastructure (totalling more than 100,000
computing cores and 40PB of disk storage) and Amazon EC2. CBRAIN
transiently stores about 10 million files representing over 50TB
distributed in 42 servers. 56 data processing applications are integrated and
over 340,000 processing batches have been submitted since 2010.

Applications in CBRAIN are integrated as Ruby classes that create web
forms, validation and execution code. The Boutiques support in CBRAIN
is based on a set of templates that generate such classes from the
application manifest. Two integration modes are available to integrate
Boutiques applications: (1) the application manifest is stored in a
CBRAIN plugin, and the Ruby classes are generated on-the-fly when
CBRAIN starts. This mode allows CBRAIN developers to add new features
to all Boutiques applications (e.g. improved error message reporting)
by updating the Ruby templates. It is, however, constrained to the
Boutiques manifest schema: features not supported in Boutiques, e.g.,
cluster-specific adjustments, cannot be supported. (2) CBRAIN Ruby
classes are generated from the Boutiques manifest in an offline
process and integrated in CBRAIN as any other application. This mode
allows developers to customize applications by editing the generated
Ruby classes, but the resulting applications are difficult to maintain
in the long term, in particular when the manifests are updated.

A custom property (\texttt{cbrain:inherits-from-class}) was added to
the Boutiques manifest to define the Ruby class that should be used as
parent class for the application in CBRAIN. It provides more
flexibility to the first integration model described previously. For
instance, it was used to define a progress bar for PSOM pipelines in
CBRAIN.

@@

A new list mechanism was also introduced in CBRAIN to facilitate the
iteration of Boutiques applications on large sets of files. CBRAIN
lists are specific files that contain references to other CBRAIN
files. When a list is passed to a Boutiques application, the elements
in the list are either concatenated in a single command line (when the
corresponding Boutiques input is a list), or a new command line is
generated for every element in the list (when the input is not a
list). Supporting lists as a specific CBRAIN file type allows for
improved validation, e.g. lists that contain references to
non-existent or deleted files can be detected. It also allows users to
edit lists using their own tools such as scripts or spreadsheet
applications.

\subsection{Flywheel}

@@

\subsection{Pegasus}

@@

\subsection{SPINE}

@@

\subsection{VIP}

>>>>

CBRAIN~\cite{SHER-14} is a web platform that can process data
distributed into multiple storage locations on computing clusters and
clouds. CBRAIN offers transparent access to remote data sources,
distributed computing sites, and an array of processing and
visualization tools within a controlled, secure environment.  The
CBRAIN service deployed at the Montreal Neurological Institute relies
on the infrastructure provided by Compute Canada~\cite{das2016mni}. It
currently provides 460+ collaborators in 20 countries with web access
to several systems, including 6 clusters of the Compute Canada
high-performance computing infrastructure (totaling more than 100,000
computing cores and 40PB of disk storage) and Amazon EC2. CBRAIN
transiently stores about 10 million files representing over 50TB
distributed in 42 servers. 56 data processing applications are integrated and
over 340,000 processing batches have been submitted since 2010.

Applications in CBRAIN are integrated as Ruby classes that create web
forms, validate parameters and run command lines on computing
resources. \boutiques is supported through a set of templates that
generate such classes from the application manifest. Two application
integration modes are available:
\begin{enumerate}
  \item The manifest is stored in a CBRAIN plugin and the Ruby classes
    are generated on-the-fly when CBRAIN starts. This mode allows
    CBRAIN developers update all Boutiques applications at once by
    editing the templates. However, it does not allow for
    customization beyond the Boutiques schema.
  \item Ruby classes are generated from manifests
    through an offline process and integrated in CBRAIN as any other
    application. This mode allows developers to customize applications
    by editing the generated Ruby classes, but the resulting
    applications are difficult to maintain in the long term, in
    particular when the manifests are updated.
\end{enumerate}

A custom property (\texttt{cbrain:inherits-from-class}) was added to
the Boutiques manifest to define the Ruby class that should be used as
parent class for the application in CBRAIN. It provides more
flexibility to the first integration model described previously.

@@

A new list mechanism was also introduced in CBRAIN to facilitate the
iteration of Boutiques applications on large sets of files. CBRAIN
lists are specific files that contain references to other CBRAIN
files. When a list is passed to a Boutiques application, the elements
in the list are either concatenated in a single command line (when the
corresponding Boutiques input is a list), or a new command line is
generated for every element in the list (when the input is not a
list). Supporting lists as a specific CBRAIN file type allows for
improved validation. For instance, lists that contain references to
non-existent or deleted files can be detected. It also allows users to
edit lists using their own tools such as scripts or spreadsheet
applications.

\subsubsection{Flywheel}

@@

\subsubsection{Pegasus}

@@

\subsubsection{SPINE}

@@

\subsubsection{VIP}
